Making Sequential Programs Deterministic

### 2019-04-06 design.tex
edits

\noindent
The type of \<get> ensures that if either the list or the index is (order)
non-deterministic, then the result of the call is nondeterministic.

@@

This is especially useful in preventing methods from non-deterministically modifying the state
of a deterministic receiver.
The correct type for \<set> on \ptype{List}{String} is

>>>>

\noindent
The type of \<get> ensures that if either the list or the index is (order)
nondeterministic, then the result of the call is nondeterministic.

@@

This is especially useful in preventing methods from nondeterministically modifying the state
of a deterministic receiver.
The correct type for \<set> on \ptype{List}{String} is

### 2019-04-06 related.tex
edits

Several techniques have been proposed to test whether a
deterministic implementation conforms to its non-deterministic finite state machine~\cite{Petrenko1996,Petrenko:1993:NSM:648128.761244,Savor:1997:639710,Hierons:2004:TCD:1040993.1040998}.
\cite{Cook:2013:RNP:2491956.2491969} presents an approach that can automatically verify properties
in branching time temporal logic systems that are inherently
non-deterministic.
Bocchino et
al.~\cite{Bocchino:2009:TES:1640089.1640097,Bocchino:2011:SND:1926385.1926447}
provide a type-and-effect system that provides compile-time determinism
guarantees for parallel programs, with a focus on barrier removal,
reasoning about interference and thread interleavings.
We believe our work to be the first verification approach
aimed at ensuring determinism in sequential programs.

>>>>

Several techniques have been proposed to test whether a
deterministic implementation conforms to its nondeterministic finite state machine~\cite{Petrenko1996,Petrenko:1993:NSM:648128.761244,Savor:1997:639710,Hierons:2004:TCD:1040993.1040998}.
\cite{Cook:2013:RNP:2491956.2491969} presents an approach that can automatically verify properties
in branching time temporal logic systems that are inherently
nondeterministic.
Bocchino et
al.~\cite{Bocchino:2009:TES:1640089.1640097,Bocchino:2011:SND:1926385.1926447}
provide a type-and-effect system that provides compile-time determinism
guarantees for parallel programs, with a focus on barrier removal,
reasoning about interference and thread interleavings.
We believe our work to be the first verification approach
aimed at ensuring determinism in sequential programs.
